\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2019-05-17 doc/paper.tex
Updated abstract wording

\singlespacing
\begin{abstract}
\noindent
Political instability is commonly thought to discourage investment and reduce economic growth. By contrast, we find that different types of ``irregular'' regime changes - coups, assassinations, or resignations - have disparate effects on stock returns. We examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability. Using a constant mean return event study model, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%). The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more. Volatility increases during times of protest preceding resignations, but no clear directionality is present. We therefore find that the expected direction and magnitude of abnormal returns is dependent on the type of political event and its expected impact on economic policy. 
\end{abstract}
\doublespacing

>>>>

\singlespacing
\begin{abstract}
\noindent
Political instability is commonly thought to discourage investment and reduce economic growth. By contrast, we find that different types of ``irregular'' regime changes - coups, assassinations, or resignations - have disparate effects on stock returns. We examine daily returns of national stock indices in every country that experienced an irregular regime change subject to data availability. Using an event study approach, we show that abnormal returns following resignations are large and positive (4\%), while those following assassinations are negative and smaller in magnitude (2\%). The impact of coups tends to be negative (2\%), but some events result in positive abnormal returns of 10\% or more. Volatility increases during times of protest preceding resignations, but no clear directionality is present. We therefore find that the expected direction and magnitude of abnormal returns is dependent on the type of political event and its expected impact on economic policy. 
\end{abstract}
\doublespacing
